Modeling the impact of IT- and AI-related emissions in a university setting.

### 2025-08-01 doc/paper.tex
Checkpoint

approximately $6.3\%$ of total emissions in 2024 \cite{uzh:sustainability:report},

artificial intelligence (AI) applications are being adopted at historically high rates exceeding those of the adoption of the personal computer and the internet \cite{bick:ai:adoption}.

>>>>

Information technology accounts for over 5\% of global electricity consumption and at least 1.7\% of global carbon emissions (estimates range from 1.5 to 4\%) \cite{wb:itu:ict}. At the University of Zürich, which with over 38,000 students and staff is the largest Swiss university, IT accounted for about 1.5 Mt CO$_2$e of greenhouse gas (GHG) emissions, approximately 6.3\% of total university emissions in 2024.\cite{uzh:sustainability:report}. The cited report takes into account university-owned workstations, servers, and audiovisual equipment, but does include other IT-related activities such as networking, cloud computing, or the growing use of artificial intelligence, and in particular generative AI and large language models (LLMs).

AI applications are being adopted at historically high rates, more quickly than the personal computer or the internet were adopted in the past\cite{bick:ai:adoption}. Enterprise AI adoption has accelerated, with generative AI tools seeing widespread deployment across industries within months of their release \cite{mckinsey2024ai}. iea:ai:energy
